The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
e.g.

Unlike traditional monolayer social networks, multilayer networks explicitly
consider social systems across contexts, including scale-dependent contexts
[@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
representing (i) different classes of individuals, e.g. male or female; (ii)
types of behaviours, e.g. grooming, travelling, or foraging; and (iii) spatial
areas, e.g. local or regional, or temporal windows, e.g. daily or seasonal
[@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
studies of animal behaviour [@Silk_2018; @Finn_2019], although they have been
used to describe multidimensional human social systems, complex transportation
networks, and neural networks [@Silk_2018]. The role of scale within multilayer
social networks remains unexplored but provides a unique opportunity to develop
novel understanding of variation in the temporal or spatial scales associated
with social systems.

@@

(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.  Individual caribou (n = `r DT[, uniqueN(get(idcol))]`) are show as nodes and each indiviual is represented by a unique color. Six layers represent combinations of two seasons (winter and summer) and three habitat classes (open, forest and forage). Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI). Interlayer edges connect individuals to themselves across seasons and within habitat classes (eg. individual "A" in summer, forest and individual "A" in winter, forest).

@@

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
fixed rate, eg. every $x$ minutes or hours, continuously throughout the study
period. We investigated the influence of the number of observations on resulting
multilayer networks. We randomly selected 500 timesteps and iteratively included
25 additional observations, regenerating the multilayer network and calculating
associations of individuals. Subsequent iterations included the previous set of
observations to mimic collection of observational data. <!-- TODO: bah conclude
/ this sentence falls off a cliff -->

>>>>

Unlike traditional monolayer social networks, multilayer networks explicitly
consider social systems across contexts, including scale-dependent contexts
[@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
representing (i) different classes of individuals, e.g. male or female; (ii)
types of behaviours, e.g. grooming, travelling, or foraging; and (iii) spatial
areas, e.g. local or regional, or temporal windows, e.g. daily or seasonal
[@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
studies of animal behavior [@Silk_2018; @Finn_2019], although they have been
used to describe multidimensional human social systems, complex transportation
networks, and neural networks [@Silk_2018]. The role of scale within multilayer
social networks remains unexplored but provides a unique opportunity to develop
novel understanding of variation in the temporal or spatial scales associated
with social systems.

@@

(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.  Individual caribou (n = `r DT[, uniqueN(get(idcol))]`) are show as nodes and each indiviual is represented by a unique color. Six layers represent combinations of two seasons (winter and summer) and three habitat classes (open, forest and forage). Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI). Interlayer edges connect individuals to themselves across seasons and within habitat classes (e.g. individual "A" in summer, forest and individual "A" in winter, forest).

@@

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
fixed rate, e.g. every $x$ minutes or hours, continuously throughout the study
period. We investigated the influence of the number of observations on resulting
multilayer networks. We randomly selected 500 timesteps and iteratively included
25 additional observations, regenerating the multilayer network and calculating
associations of individuals. Subsequent iterations included the previous set of
observations to mimic collection of observational data. <!-- TODO: bah conclude
/ this sentence falls off a cliff -->
